The Topic Browser\\An Interactive Tool for Browsing Topic Models

### 2010-11-10 masters_thesis/browser_nips/paper.tex
Updates for the final version of the browser paper

\title{The Topic Browser\\An Interactive Tool for Browsing Topic Models}
\author{
Matthew J. Gardner \\
Department of Computer Science \\
Brigham Young University \\
\texttt{mjg82@byu.edu} \\
\And
Joshua Lutes \\
Department of Computer Science \\
Brigham Young University \\
\texttt{jlutes@byu.edu} \\
\And
Jeff Lund \\
Department of Computer Science \\
Brigham Young University \\
\texttt{jefflund@gmail.com} \\
\And
Josh Hansen \\
Department of Computer Science \\
Brigham Young University \\
\texttt{jjfresh@byu.edu} \\
\And
Dan Walker \\
Department of Computer Science \\
Brigham Young University \\
\texttt{danwalkeriv@gmail.com} \\
\And
Eric Ringger \\
Department of Computer Science \\
Brigham Young University \\
\texttt{ringger@cs.byu.edu} \\
\And
Kevin Seppi \\
Department of Computer Science \\
Brigham Young University \\
\texttt{kseppi@cs.byu.edu} \\
}

@@

While our tool is still under development, a description of the Topic Browser,
a working demo, and the current version of the code are available at
http://nlp.cs.byu.edu/topic\_browser [Note to reviewers: this is currently just
a demo of the browser; by the time of the workshop it will have the description
and code mentioned].  Our tool currently supports any topic model that labels
individual tokens in the corpus with topics, and is built to import data
directly from MALLET input and output files~\cite{mallet}, or files similarly
formatted.  We have plans to include specialized visualizations for more
complicated topic models, such as Topics over Time, sentiment-topic models,
hierarchical topic models, and others.

>>>>

\title{The Topic Browser\\An Interactive Tool for Browsing Topic Models}
\author{
M. Gardner, J. Lutes, J. Lund, J. Hansen, D. Walker, E. Ringger, and K. Seppi\\
Department of Computer Science \\
Brigham Young University \\
\texttt{mjg82@byu.edu} \\
}

@@

While our tool is still under development, a description of the Topic Browser,
a working demo, and the current version of the code are available at
http://nlp.cs.byu.edu/topic\_browser.  Our tool currently supports any topic
model that labels individual tokens in the corpus with topics, and is built to
import data directly from MALLET input and output files~\cite{mallet}, or files
similarly formatted.  We have plans to include specialized visualizations for
more complicated topic models, such as Topics over Time, sentiment-topic
models, hierarchical topic models, and others.
